### 2014-02-14 paper/cesk.tex
idea of guard on what can be labeled from the target language

\begin{enumerate}
 \item What is this saying? In any evaluation context $\TE$ the value
 \Tv reduces to the same configuration regardless of the store (and
 environment).
 \item We must consider the evaluation in the combined language; this
 e.g., allows labeling already-labeled values.
 \item The typing rule $\forall \Delta, \Gamma. \Delta;\Gamma \vdash
 \Tv : \tau$ is necessary when we want to preserve the type of \Tv,
 but no sufficient (e.g., can have same values of same type, but
 different value in the store; hence, we also need the SOS condition).
 \item The stronger condition: $\cdot \vdash \Tv : \tau$ implies the
 SOS condition.
\end{enumerate}

>>>>

\begin{enumerate}
 \item What is this saying? In any evaluation context $\TE$ the value
 \Tv reduces to the same configuration regardless of the store (and
 environment).
 \item We must consider the evaluation in the combined language; this
 e.g., allows labeling already-labeled values.
 \item The typing rule $\forall \Delta, \Gamma. \Delta;\Gamma \vdash
 \Tv : \tau$ is necessary when we want to preserve the type of \Tv,
 but no sufficient (e.g., can have same values of same type, but
 different value in the store; hence, we also need the SOS condition).
 \item The simpler condition: $\cdot \vdash \Tv : \tau$ for typed
 langauges may be easier to user; in this case the embedder needs to
 only prove that this implies the SOS condition.
 \item Really we want to add a meta-level function $\nu: \Tv
 \rightharpoonup \Tv$; this allows adding more ``guards'' for what can
 be labled. In the case of Browbound, $\nu$ can, for example, throw an
 exception if the value is not a string, thus forcing the programmer
 to only pass in stringyfied data. In turn, proving that the condition
 holds for this subset of values (strings) is trivial.

\end{enumerate}
